Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-23 cordillera-cycle.tex
Add notes for co-authors.

% My commands
\def\idea#1{\textcolor[rgb]{0,0.5,0}{\textbf{[IDEA: #1]}}}
\def\todo#1{\textcolor[rgb]{0.5,0,0}{\textbf{[TODO: #1]}}}
\def\aref{\textcolor[rgb]{0.5,0,0}{\textbf{[REF]}}}
\def\citep#1{}
\def\citet#1{}

@@

@@

@@

@@

@@

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{\textbf{(top)} temperature offset time-series from ice and sediment
           core records used as palaeo-climate forcing for the ice sheet model
           (Table~\ref{tab:records}). \textbf{(bottom)} Modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent. The grey spans indicate the ranges of modelled times of
           glacial extrema corresponding to MIS~4 (61.9--55.4\,\unit{kyr}), 3
           (52.2--45.6\,\unit{kyr}), and 2 (last glacial maximum,
           29.5--16.9\,\unit{kyr}).}
  \label{fig:timeseries}
\end{figure}

>>>>

% My commands
\def\idea#1{\textcolor[rgb]{0,0.5,0}{\textbf{[IDEA: #1]}}}
\def\note#1{\textcolor[rgb]{0,0,0.5}{\textbf{[NOTE: #1]}}}
\def\todo#1{\textcolor[rgb]{0.5,0,0}{\textbf{[TODO: #1]}}}
\def\aref{\textcolor[rgb]{0.5,0,0}{\textbf{[REF]}}}
\def\citep#1{}
\def\citet#1{}

@@

\note{Please read through the abstract, introduction and figure captions. All
      other sections are very preliminary at this stage. I need some feedback
      on the (currently embryonic) discussion part.}

@@

\note{Currently, this section contains parts from the previous paper.}

@@

\note{At this stage, this section is just a collection of thoughts that need to
be developed into paragraphs. Please comment, criticize, add your own ideas.}

@@

\note{Nothing here at the moment.}

@@

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{\textbf{(top)} temperature offset time-series from ice and sediment
           core records used as palaeo-climate forcing for the ice sheet model
           (Table~\ref{tab:records}). \textbf{(bottom)} Modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent. The grey spans indicate the ranges of modelled times of
           glacial extrema corresponding to MIS~4 (61.9--55.4\,\unit{kyr}), 3
           (52.2--45.6\,\unit{kyr}), and 2 (last glacial maximum,
           29.5--16.9\,\unit{kyr}).
           \note{The dotted line represents an ongoing 5km-resolution
           simulation, which may be eventually be used in
           Figs.~\ref{fig:duration} and \ref{fig:deglac}.}}
  \label{fig:timeseries}
\end{figure}
